\normalfont \normalsize \textsc{Harvard University} \\[25pt] \textsc{CS281} \\[25pt] \horrule{0.5pt} \\[0.1cm] \huge Final Project Update: \\ \huge Classification for the Yelp Data Set Challenge \horrule{2pt} \\[0.5cm]

### 2015-12-08 latex/poster_parts.tex
supervised learning

>>>>

\section{Classification}

Once the feature has been extracted, we can apply supervised learning methods to classify the Yelp restaurants based on their labels on Yelp. Several approaches are possible with regards to the features to solve this multi-labels classigication task

\subsection*{Features}

The features are divided into two main parts: on one hand, the topics assignements extracted from the reviews with the LDA and on the other hand, the properties provided by Yelp. Pre-processing the latter part provided a 198 dimensionnal vector. These features contain both numerical features (rating, space coordinates, number of reviews, customer check-in...) and categorical features converted into indicator variables.

\subsection*{Methods}

The outputs of our classification are the labels of each restaurant. We chose to train several binary classifiers to predict one label at a time with a One-Vs-All approach. The high dimensionnality of the features and the large number of indicator varibales induces a high sparsity. As a result, a sufficiently robust algorithm need to be used. One particularity is also that the classes are all really skewed, the dummy baseline where we do not predict  any label for all the restaurant has a really high score.\\

\begin{center}
    \begin{tabular}{| l | l | l | l |}
    \hline
    & OVI LDA & GS LDA & NMF \\ \hline
    All False & 90,02 \% &  90.02 \% &  90.02 \% \\ \hline
    kernel rbf SVM & 90,81\% &  90.38\% &  90.38\% \\ \hline
    kernel rbf SVM + PCA & 90.83\% &  90.60\% &  90.57\% \\ \hline
    Logistic Regression & 90.84\% &  91.89\%  &  91.24\%\\ \hline
    Logistic Regression + PCA & 92.59\% &  92.53\% &  92.68\% \\ \hline
    Lasso & 90.82\% &  93.44\% &  92.01\% \\ \hline
	Lasso + PCA & 93.44\%  &  \textbf{94.46} \%  &  93.08\% \\ \hline
    Random Forest & 91.90\% &  93.31\% &  92.89\% \\ \hline
    Random Forest + PCA & 93.63\% &  94.04\% &  93.44\% \\ \hline
    \end{tabular}
\end{center}

We first coded a l2 regularized logistic regression and use scikit learn for the other methods. The random forest provides the best predictor expected as it corresponds to an ensemble method that combines multiple decision trees, leading to a more robust model. We showed the ROC curves that we obtained. The variance of the classifiers with regards to the class used as output is quite high. This could be explained by the relative skewness of each class and also their own specificity. Moreover, using dimensionality reduction method on the Yelp check-ins information before the classificationthe PCA also improved the accuracy. These features contains the average number of customers for each hour of the week which leads to a vector of dimension 168. The principal component analysis dropped it down to 13, while keeping 94\% of the variance.

\begin{figure}[H]
	\includegraphics[scale=0.55]{img/roc_lasso.png}
	\centering
\end{figure}

\begin{figure}[H]
	\includegraphics[scale=0.55]{img/roc_rf.png}
	\centering
\end{figure}

Moreover, this method provides a way to sort the features by importance.\\

FEATURES IMPORTANCE
